DeepRain

### 2019-08-24 Docs/Langdokumentation.tex
A4 paper size
Added ToDo
Added "Datanaufbereitung" documentation, added packages to main tex

\documentclass[11pt]{article}

@@

\usepackage[english,ngerman]{babel}                 % German and English word separation settings
\usepackage[autostyle=true,german=quotes]{csquotes} % Better German quotes
\usepackage{graphicx}                               % Include graphics/images
\usepackage{multirow}                               % Row spanning over multiple rows
\usepackage{subcaption}                             % Used for 2 images side-by-side
\usepackage[bookmarks,                 % Creates bookmarks
            bookmarksnumbered=true,    % Numbers in PDF bookmarks
            bookmarksopen=true,        % Don't show bookmaks when opened
            hyperindex=true,           % Numbers in index are links
            pdfpagelabels=true,        % Set PDF page labels
            pdfa]{hyperref}                     % Klickable Links and ToC entries (should be last package !!!)

\hypersetup{
    pdfauthor           = {Thomas Gnaedig, Etienne Gramlich, Tim, Merle Wolf},
    pdftitle            = {DeepRain},
    pdfsubject          = {Deep Learning},
    pdfkeywords         = {Deep Learning,rain},
    pdflang             = {de},         % Set language of document to German
    pdfstartview        = {FitH},       % Fit the document to screen horizontally (page width)
    pdfview             = {FitH},       % Fit the document to screen horizontally (page width)
    colorlinks          = {true},       % Use color for links
    linkcolor           = {black},      % Links in black (text color)
    urlcolor            = {black},      % URLs in black (text color)
    citecolor           = {black},      % Citations in black (text color)
    filecolor           = {black},      % File links in black (text color)
}

\title{DeepRain}
\author{Thomas Gnaedig, Etienne Gramlich, Tim, Merle Wolf}

@@

% Datenaufbereitung

@@

>>>>

\documentclass[11pt,a4paper]{article}

@@

\usepackage[english,ngerman]{babel}                 % German and English word separation settings
\usepackage[autostyle=true,german=quotes]{csquotes} % Better German quotes
\usepackage{graphicx}  
\usepackage{float}                             % Include graphics/images
\usepackage{multirow}                               % Row spanning over multiple rows
\usepackage{subcaption}                             % Used for 2 images side-by-side
\usepackage{tabularx} % for 'tabularx' environment
\usepackage[bookmarks,                 % Creates bookmarks
            bookmarksnumbered=true,    % Numbers in PDF bookmarks
            bookmarksopen=true,        % Don't show bookmaks when opened
            hyperindex=true,           % Numbers in index are links
            pdfpagelabels=true,        % Set PDF page labels
            pdfa]{hyperref}                         % Klickable Links and ToC entries (should be last package !!!)

\hypersetup{
    pdfauthor    = {Thomas Gnaedig, Etienne Gramlich, Tim Hardenacke, Merle Wolf},
    pdftitle     = {DeepRain},
    pdfsubject   = {Deep Learning},
    pdfkeywords  = {Deep Learning,rain},
    pdflang      = {de},         % Set language of document to German
    pdfstartview = {FitH},       % Fit the document to screen horizontally (page width)
    pdfview      = {FitH},       % Fit the document to screen horizontally (page width)
    colorlinks   = {true},       % Use color for links
    linkcolor    = {black},      % Links in black (text color)
    urlcolor     = {black},      % URLs in black (text color)
    citecolor    = {black},      % Citations in black (text color)
    filecolor    = {black},      % File links in black (text color)
}

\title{DeepRain}
\author{Thomas Gnaedig, Etienne Gramlich, Tim Hardenacke, Merle Wolf}

@@

% Datenaufbereitung
\input{Datenaufbereitung.tex}

@@

% Ziel und Test: MSE
